---
title: "Final Project"
author: "Emily Fernandez"
date: "12/14/2021"
output: html_document
---
## Libraries
```{r, message = FALSE}
install.packages("tidyverse")
library(tidyverse)
install.packages("dplyr")
library(dplyr)
install.packages("tidyr")
library(tidyr)
install.packages("modelr")
library(modelr) 
```

### Introduction

My topic is video games and general information about each game uploaded in Steam, an online gaming platform. Some of this information includes name of the game, developers, publishers, required age, price, etc.

My questions were:

1. Are games that have a required age of 0 more expensive than those with a required age of 18? 
2. Is there a difference in the average price of games available in English and those not available in English?
3. Do the developers that make more games charge higher prices? 


The answers were:

1. More expensive games have a required age of 18. However, games with age requirements of 7 and 17 contain the most expensive games overall. 
2. Yes, there is a difference between the average price of games available in English and those that are not available in English. The average price of games in English is about 7.50 whereas the average price of games not in English is about 4.20.
3. Yes, there is a small positive relation between the number of games a developer has and the average price of their games, however my model was not a good model, so these results are not significant.

&nbsp;

### Data Source

The data that I am using came from the website Kaggle, which consists of publicly available data sets. The URLs for the data sets that I accessed are https://www.kaggle.com/nikdavis/steam-store-raw/version/1?select=steam_app_data.csv and https://www.kaggle.com/nikdavis/steam-store-raw/version/1?select=steam_app_data.csv. These particular data sets are publicly available for everyone to access but I altered the data sets slightly to make it easier to format. This information from steam_data was collected by downloading the Steam Store API. The second data set, steamspy_data was downloaded by SteamSpy, a service that provides information on games uploaded on Steam.

&nbsp;

### Ethics Reflection

There are no ethical issues to consider related to how my data was gathered or to my analysis. There is a possibility of ethical issues resulting if someone used this data in a different way. Fairness and Justice may be violated if someone uses this data to create a program or bot to help them win a game. Using a bot that utilizes the information in these data sets creates an unfair advantage.

&nbsp;

### Data Import

_Data Set 1_
```{r}
steam_data <- read_csv("steam_data.csv") %>% # Uploading the data set into R
  rename(publisher = publishers, 
         appid = steam_appid,
         developer = developers) %>% # Renaming these column names to match the other tibble
  mutate(across(appid, as.double)) %>%  # Change the type variable of appid to match the steam_appid from other tibble
  mutate(across(required_age, as.factor)) %>%  # Changing the type variable to factor %>% 
  mutate(across(c("publisher", "developer"), str_replace_all, "\\['|\\']", "")) %>% # Remove the ['    '] in publisher and developer rows 
  select (type, name, appid, required_age, is_free, controller_support, developer, publisher) # Selecting only the columns that have values in them
steam_data
```


_Data Set 2_
```{r}
steam_spy_data <- read_csv("steamspy_data.csv") %>% # Uploading the data set into R
 mutate (english = case_when(
            grepl(pattern = "English", x = languages) ~ "Yes", # grepl function replaces matches of a pattern
            grepl(pattern = "!English", x = languages) ~ "No" )) %>% # making a new column that says whether the game is available in English (Yes) or not (No)
 mutate(across(c(price, initialprice, discount),  ~.x/100)) %>%  # adjusting the numbers to include the decimal point
    select( -(languages) ) # select all columns except languages
steam_spy_data
```
&nbsp;

### Data Tidying

```{r}
steam_data_final <- left_join(steam_data, steam_spy_data, by = c("appid", "name", "developer", "publisher")) # Doing a left join to combine the two data sets by the appID of the game that appear in both tibbles
steam_data_final
```

&nbsp;

### Data Exploration

_Visualization of Question 1_

Are games that have lower prices more likely to have a required age of 0 or 18?

```{r}
q1 <- steam_data_final %>% 
  group_by(required_age) %>% # Grouping by required age
  summarize(num_ages = n(), avg_price = mean(price, na.rm = TRUE)) %>% # Using summarize to calculate the average price of games based on the required age
  ggplot() + geom_bar(aes(x = required_age, y = avg_price), stat = "identity", fill = "light blue") + xlab("Age Requirement") + ylab("Average Price") + ggtitle("Average Price of Games by Required Age")# Plotting the required age on x axis and the average price on y axis of a bar chart
q1
```
_Visualization of Question 2_

Is there a difference in the average price between games available English and those not available in English?

```{r}
q2 <- steam_data_final %>% 
  group_by(english) %>% # Grouping by English by having the english and No english section
  summarize(num_english = n(), avg_price = mean(price, na.rm = TRUE)) %>% # Using summarize to calculate the average price of games based on whether the game is in English or not
  ggplot() + geom_bar(aes(x = english, y = avg_price), stat = "identity", fill = "light blue") + xlab("English Availability") + ylab("Average Price") + ggtitle("Average Price of Games by English Availability") # Plotting the English/No English data on x axis and the avg price on y axis of a bar chart
q2
```

```{r}
steam_data_final %>% 
 group_by(english) %>% 
  summarize(num_english = n(), avg_price = mean(price, na.rm = TRUE)) # To see exact numbers of the price averages of both categories
```

&nbsp;

_Transformation and Modeling of Question 3_

Do the developers that make more games charge higher prices? 

```{r}
dev_data <- steam_data_final %>% 
  group_by(developer) %>% # grouping by developer 
  summarize(num_games = n(), avg_price = mean(price, na.rm = TRUE)) %>% # Calculating the average price of games based on the number of games a developer makes
  arrange(desc(num_games))
dev_data
```

```{r}
mod_dev <- lm(avg_price ~ num_games, data = dev_data) # creating a linear model based on the average price and the number of games
mod_dev
```

```{r}
grid_dev <- dev_data %>% 
  data_grid(num_games) %>% # Collecting the number of games
  add_predictions(mod_dev) # Adding the predictions of the model
grid_dev
```

```{r}
res<- dev_data %>% add_residuals(mod_dev) # Adding the residuals of the model
res
```

```{r}
full_join(grid_dev, res) # Joining these in one table
```

```{r}
dev_data %>% ggplot() +
  geom_point(aes(num_games,avg_price), alpha = 1/3) +
  geom_line(aes(x = num_games, y = pred), data = grid_dev, color = "red", size = 1) + xlab("Number of Games") + ylab("Average Price") + ggtitle("Price of Games based on Number of Games Published") # Plotting the model
```

&nbsp;

_Taking out outliers_

```{r}
dev_data2 <- steam_data_final %>% 
  group_by(developer) %>% # grouping by developer 
  summarize(num_games = n(), avg_price = mean(price, na.rm = TRUE)) %>% # Calculating the average price of games based on the number of games a developer makes
  filter(num_games <= 50, avg_price <= 100) #filtering out the outliers of the previous model
dev_data2
```

```{r}
mod_dev <- lm(avg_price ~ num_games, data = dev_data2) # creating a linear model based on the average price and the number of games
mod_dev
```

```{r}
grid_dev2 <- dev_data2 %>% 
  data_grid(num_games) %>% # Collecting the number of games
  add_predictions(mod_dev) # Adding the predictions of the model
grid_dev2
```

```{r}
res2 <- dev_data2 %>% add_residuals(mod_dev) # Adding the residuals of the model
res2
```

```{r}
full_join(grid_dev2, res2) # Joining these in one table
```

```{r}
dev_data2 %>% ggplot() +
  geom_point(aes(num_games,avg_price), alpha = 1/3) +
  geom_line(aes(x = num_games, y = pred), data = grid_dev2, color = "red", size = 1) + xlab("Number of Games") + ylab("Average Price") + ggtitle("Price of Games based on Number of Games Published")# Plotting the model
```


```{r}
res2 %>% ggplot() +
  geom_point(aes(num_games, resid), alpha = 1/3) + xlab("Number of Games") + ylab("Residuals") # Plotting the residuals
```
&nbsp;




### Conlusion

In my analysis I answered three different questions based on my data set. This data set contains information of games uploaded on Steam. My first question was asking whether games that have a required age of 0 are more expensive than those with a required age of 18. I found that games with a required age of 18 were more expensive than games that have a required age of 0. Overall, the most expensive games have an age requirement of 7 and 17. The second question I analyzed was whether there was a difference in the average price of games available in English and those that were not. I found that games in English had a higher game price average. The average price for games in English is about 7.50 dollars and the average price for games not in English is about 4.20 dollars.

My final question was testing whether developers with more games were more likely to have more expensive games. I found that there was a small positive relationship between these two variables in my linear model. There were very large outliers in the data, which may have affected the overall relationship. I then altered my model to exclude the outliers and I found that the plot was still not very readable. Afterwards I plotted the residuals and it was very similar to the second plot of my data. In conclusion, this model was not a good one. Some next steps that I would take is to attempt to make this a quadratic model to see if it is a better fit for the data.

Some limitations of this data is that there was some missing information throughout the entire data set for some of the games. In addition, in regards to my linear model and my second question, it may not be accurate in other countries. Steam has different prices and listings for games in other countries and in other currencies. Some next steps may be to try to find the missing values in the data set. Furthermore, it may be interesting to see if the trends that I analyzed still hold up in other countries. Especially the questions pertaining to games not available in English and the average price of games based on the developers.


